---
output:
    html_notebook:
        toc: true
        toc_float: true
editor_options:
  chunk_output_type: inline
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(devtools)
```

# `saperlipopette` - package editor checks

## **Editor:** [\@robitalec](https://github.com/robitalec)

### Date:
**`r cat(sprintf("**Last updated:** %s", Sys.Date()))`**

***

<br>

This report documents the editor checks of **rOpenSci** submitted package:

### **`saperlipopette`: ropensci/software-review**  issue [\#754](https://github.com/ropensci/software-review/issues/754).

<br>

## Package info

**Description:**

Holds functions creating Git messes, that users would then
    solve, to follow <https://ohshitgit.com/>.

**Author:** `r c(
    person("Maëlle", "Salmon", , "msmaellesalmon@gmail.com", role = c("cre", "aut"),
           comment = c(ORCID = "0000-0002-2815-0399")),
    person("Jim", "Gardner", role = "ctb"),
    person("Yanina Bellini", "Saibene", role = "aut",
           comment = c(ORCID = "0000-0002-4522-7466")),
    person("Steffi", "LaZerte", role = "rev",
           comment = c("Steffi reviewed the 'saperlipopette, a risk-free playground for learning more Git' article.", ORCID = "0000-0002-7690-8360"))
  )`

**repo url:** <https://docs.ropensci.org/saperlipopette/,
    https://github.com/ropensci-training/saperlipopette>

**website url:** <https://docs.ropensci.org/saperlipopette/>

## Review info


#### See [editors guidelines](https://ropensci.github.io/dev_guide/editorguide.html) for further information on the rOpenSci editors checks process.

**key editor checks:**



<!--Please be respectful and kind to the authors in your reviews. The rOpenSci [code of conduct](https://github.com/ropensci/onboarding/blob/master/policies.md/#code-of-conduct) is mandatory for everyone involved in our review process.-->


***

### session info


```{r sessionInfo}
sessionInfo()
```


```{r pkg_dir, echo = F}
pkg_dir <- "/home/alecr/Documents/Local-git/saperlipopette"
```

## Test installation

### test local `saperlipopette` install:

```{r test-local}
install(pkg_dir, dependencies = TRUE, build_vignettes = TRUE)
```

```{r github-rm}
remove.packages("saperlipopette")
```
#### **comments:**

no issues

***

### test install of `saperlipopette` from GitHub with:

```{r test-github}
devtools::install_github("ropensci-training/saperlipopette", dependencies = TRUE, build_vignettes = TRUE)
```

#### **comments:**

no issues

***



## Check package integrity

### run checks on `saperlipopette` source:

```{r check-checks}
devtools::check(pkg_dir)
```
#### **comments:**

no issues

***

### run tests on `saperlipopette` source:

```{r check-tests}
devtools::test(pkg_dir)
```
#### **comments:**

```r
R: library(saperlipopette)
R: 
R: devtools::test('../saperlipopette')
ℹ Testing saperlipopette
✔ | F W  S  OK | Context
✖ | 1        1 | blame                                                                          
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-blame.R:6:3): exo_blame() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "99738a808b6d5529d8de83fb20c0588ec5afff41"
+   [1] "e776cc8573afe6cb331159e4b9113ac60d49709e"
-   [2] "a334b44fc56f21a609989b187685bbcfbcaac4d7"
+   [2] "01bdc274b5d54de9a7ab4cad8869fdbe629ebd04"
-   [3] "d5ff861dede667b9856f42417585df40d5c0fb76"
+   [3] "376f91dfb553475c7a1e7632bb342a11dcb52384"
-   [4] "595c3093fe615679519631bf045b1bdd76a729cf"
+   [4] "797d5c39d7b5e8b08f3dc4f15b4eea971dd85b19"
-   [5] "2ee32ca74a45769de57f2cf4149adff0f1d9e61b"
+   [5] "1d65bddf84e335aa3bb32f1656a103648adf3714"
-   [6] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [6] "b59b4809e7f0ec8a0df85b443baa73b332bd3b5b"
* Run testthat::snapshot_accept("blame", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("blame", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✔ |          1 | check-editor                                                                   
✖ | 1        1 | clean-dir                                                                      
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-clean-dir.R:6:3): exo_clean_dir() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "2a61d9da6865eb7f7272c9f901f13c1da377a01e"
+   [1] "aec15965c3581c3dcba6359f74c91cd54fb5939d"
-   [2] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [2] "c090f52d68d5a007775eddfe026b2e72e66eedcd"
* Run testthat::snapshot_accept("clean-dir", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("clean-dir", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | committed-to-main                                                              
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-committed-to-main.R:6:3): exo_committed_to_main() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "2ff0d31f566e68ae0ee94b6028a3fa2e24ed066a"
+   [1] "e7889516408acd1619610931f0e68a1b3c577007"
-   [2] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [2] "1f4724b272699cdc79512cf053ef9bc66feaf8ca"
* Run testthat::snapshot_accept("committed-to-main", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("committed-to-main", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | committed-to-wrong-branch                                                      
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-committed-to-wrong-branch.R:6:3): exo_committed_to_wrong() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "83ee0e3cc5afed932cd9e3f2f34274c60bfe1166"
+   [1] "380f963522865ce2be3a06d9a611cf73e2e0b23a"
-   [2] "e48ac924412914278ed7d3ee6e82d0fe3122741a"
+   [2] "56591fc55e10052367efa3cea143b9b063f4d266"
-   [3] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [3] "569711c966f498b8aa7a7554496e3a702d934568"
* Run testthat::snapshot_accept("committed-to-wrong-branch", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("committed-to-wrong-branch", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | conflict                                                                       
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-conflict.R:6:3): exo_conflict() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "5d871367c8a247a5e63bd0701d7bce830d1dc614"
+   [1] "d4f7a10710d1b61c9664303663b5fe467d9e2215"
-   [2] "2a61d9da6865eb7f7272c9f901f13c1da377a01e"
+   [2] "fe387b39814b24ba7ef653a0546b4b4796cd9357"
-   [3] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [3] "f0a62988268a33177343cde2ad009aee53f107c1"
* Run testthat::snapshot_accept("conflict", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("conflict", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        0 | create-all [3.9s]                                                              
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-create-all.R:5:3): create_all_exercises() works
Snapshot of code has changed:
     old                    | new                                   
 [3] Output                 | Output                 [3]            
 [4]                        |                        [4]            
 [5]   +-- bisect           |   +-- bisect           [5]            
 [6]   |   \-- R            -   |   +-- R            [6]            
 [7]   |       \-- script.R -   |   |   \-- script.R [7]            
                            -   |   \-- bisect.Rproj [8]            
 [8]   +-- blame            |   +-- blame            [9]            
 [9]   |   \-- R            -   |   +-- R            [10]           
[10]   |       \-- script.R -   |   |   \-- script.R [11]           
                            -   |   \-- blame.Rproj  [12]           
 ... ...                      ...                    and 11 more ...
     old                      | new                                               
[21]   |   \-- debugging      |   |   \-- debugging                [25]           
[22]   +-- committed-to-main  |   +-- committed-to-main            [26]           
[23]   |   +-- R              |   |   +-- R                        [27]           
[24]   |   \-- bla            -   |   +-- bla                      [28]           
                              -   |   \-- committed-to-main.Rproj  [29]           
[25]   +-- committed-to-wrong |   +-- committed-to-wrong           [30]           
[26]   |   +-- R              |   |   +-- R                        [31]           
[27]   |   +-- bla            |   |   +-- bla                      [32]           
                              -   |   +-- committed-to-wrong.Rproj [33]           
[28]   |   \-- fix.txt        |   |   \-- fix.txt                  [34]           
 ... ...                        ...                                and 56 more ...
* Run testthat::snapshot_accept("create-all", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("create-all", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | debug [1.6s]                                                                   
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-debug.R:6:3): exo_bisect() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-     [1] "d1e99031240ba2b6a78117f09df1c3b7b089f41a"
+     [1] "affb2beec0c0da8ffc1238e0e47d6950d538ffa3"
-     [2] "f26c132d3ab725336f321b6f0c403022e0ad7372"
+     [2] "bd69e88b0e744e568a729831caac348fb50670af"
-     [3] "85cebcf1f5c19397a19a009747353d7246979c52"
+     [3] "78f61cce1b2949633cd2d6f8878af2d3fb3616f2"
-     [4] "978a4d7a52ce0c4e5a3f82f53fff6d804f4efeeb"
+     [4] "79a6ed2bb6ee936b1bb3a0b7e48c34400d06ce56"
-     [5] "2add1f6723f3d88c68999d97b3ffebe1fe119642"
+     [5] "2f5028c4d3a11a24fe2d87f041a4ea7df14f5ed0"
-     [6] "beb2fa1f91f2cc320c2c8da9ba295e72cf0b1021"
+     [6] "b7923e30e46f9e836be467ffefed23becb97de0e"
-     [7] "4113e395ef532fd197de37528c914af919a6d90a"
+     [7] "a57f764dc0489d422e866560bd82251eff6ed3c5"
and 93 more ...
* Run testthat::snapshot_accept("debug", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("debug", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | edit-latest-message                                                            
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-edit-latest-message.R:6:3): exo_latest_message() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-   [1] "d3d35a17a880eee777868a5fbe99ce1bfe3b31bb"
+   [1] "6740f4094f9d80f2bf20cea36b16d329345b33d2"
-   [2] "e227ecc55e421f70b6e30602e6a2eee02aad42e0"
+   [2] "517cffaed99afdb2143fc9a408b08ac5ef5faca7"
* Run testthat::snapshot_accept("edit-latest-message", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("edit-latest-message", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | log-deleted-file                                                               
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-log-deleted-file.R:6:3): exo_log_deleted_file() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-    [1] "8d49564daf69f7da3208dce5db26e832d52a01d1"
+    [1] "e48a98ca70738acccbdca3de1d3da01561c1058d"
-    [2] "b6af1dca46a09968c561b22af44ad35ee4ea413b"
+    [2] "b5fd33c3575b7a50f0c1ead29f54ea3eb5d3a0f9"
-    [3] "ab0ec48cd3306cc2a29341d84d634e0264a6b558"
+    [3] "0d0c4a4ce6f30ddc63bc79be178eb9cb9dcdf905"
-    [4] "f1e91f7e99f4783a778790512d7bf8cbdbe73436"
+    [4] "87c7a33e9d944ea4337e19952654447796f790cd"
-    [5] "5b9bce029eb8363b54e257ff3c27ccca0810f181"
+    [5] "f5598c92ed9f82fefc04030e5977cf7632ff5f08"
-    [6] "7b1ad57aae390d25d0f12b6b88a5e890eb0ffead"
+    [6] "ca0126a96d2373972b97c0927fb296a201ffeacb"
-    [7] "b6ba25ffa8b4f2302f17fb5bebe7f8305c5f7834"
+    [7] "038a6954ff7f626919ff369371669f1e80cf67e2"
and 8 more ...
* Run testthat::snapshot_accept("log-deleted-file", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("log-deleted-file", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────
✖ | 1        1 | log-deleted-line                                                               
────────────────────────────────────────────────────────────────────────────────────────────────
Failure (test-log-deleted-line.R:6:3): exo_log_deleted_line() works
Snapshot of code has changed:
old vs new
  Code
    gert::git_log(repo = path)[["commit"]]
  Output
-    [1] "9162b22638c61c25790b5c60da6034928bd084ee"
+    [1] "a166ab10bf643c7eeeb6746e976a74872c3d9f9e"
-    [2] "963cbe002216fc14feddac7927594f1a160df505"
+    [2] "9993ba4d7b248076755979968ae337768753f67c"
-    [3] "5e9ace09746de941c4b177dbf8ddffdb91071ce3"
+    [3] "e88bb306477fbfca519c94f6034bfc1c1422bfd7"
-    [4] "5ea923a3ab33fda78c073ab84b9e9276777b2fca"
+    [4] "608fd6a9782dde40c73ffcf4f6b81d9d375af2cc"
-    [5] "27b8c167ba1b06a1c1758e254cf43aa060021baa"
+    [5] "35eba4dfa498c2bbc3c53ddb0b3e6c618c11e621"
-    [6] "d1e464d9da59120d4e64f3beee884ab4197aed93"
+    [6] "4ff3594c93deddd6e5818bff155bfe9ce0e9aee0"
-    [7] "544d738b703fdbdc0511beba1f622ce893e6c818"
+    [7] "c5412c2428086c62d361aff84f5c564fa9c0bd65"
and 4 more ...
* Run testthat::snapshot_accept("log-deleted-line", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to accept the change.
* Run testthat::snapshot_review("log-deleted-line", "/home/alecr/Documents/Local-git/saperlipopette/tests/testthat") to review the change.
────────────────────────────────────────────────────────────────────────────────────────────────

Maximum number of failures exceeded; quitting.
ℹ Increase this number with (e.g.) testthat::set_max_fails(Inf) 
R: 
R: sessionInfo()
R version 4.5.2 (2025-10-31)
Platform: x86_64-pc-linux-gnu
Running under: Arch Linux

Matrix products: default
BLAS:   /usr/lib/libblas.so.3.12.0 
LAPACK: /usr/lib/liblapack.so.3.12.0  LAPACK version 3.12.0

locale:
 [1] LC_CTYPE=en_CA.UTF-8       LC_NUMERIC=C               LC_TIME=en_CA.UTF-8       
 [4] LC_COLLATE=en_CA.UTF-8     LC_MONETARY=en_CA.UTF-8    LC_MESSAGES=en_CA.UTF-8   
 [7] LC_PAPER=en_CA.UTF-8       LC_NAME=C                  LC_ADDRESS=C              
[10] LC_TELEPHONE=C             LC_MEASUREMENT=en_CA.UTF-8 LC_IDENTIFICATION=C       

time zone: America/Halifax
tzcode source: system (glibc)

attached base packages:
[1] stats     graphics  grDevices utils     datasets  methods   base     

other attached packages:
[1] saperlipopette_0.1.0.9000 testthat_3.3.2           

loaded via a namespace (and not attached):
 [1] xml2_1.3.8        stringi_1.8.7     digest_0.6.37     magrittr_2.0.3    evaluate_1.0.4   
 [6] pkgload_1.4.0     fastmap_1.2.0     rprojroot_2.1.0   parsedate_1.3.2   whisker_0.4.1    
[11] pkgbuild_1.4.8    sessioninfo_1.2.3 brio_1.1.5        urlchecker_1.0.1  promises_1.3.3   
[16] purrr_1.1.0       cli_3.6.5         shiny_1.11.1      crayon_1.5.3      diffobj_0.3.6    
[21] rlang_1.1.6       ellipsis_0.3.2    remotes_2.5.0     withr_3.0.2       cachem_1.1.0     
[26] devtools_2.4.5    tools_4.5.2       memoise_2.0.1     httpuv_1.6.16     credentials_2.0.2
[31] vctrs_0.6.5       R6_2.6.1          mime_0.13         lifecycle_1.0.4   stringr_1.5.1    
[36] fs_1.6.6          htmlwidgets_1.6.4 usethis_3.1.0     miniUI_0.1.2      waldo_0.6.2      
[41] pkgconfig_2.0.3   desc_1.4.3        pillar_1.11.0     later_1.4.2       glue_1.8.0       
[46] profvis_0.4.0     Rcpp_1.1.0        gert_2.3.1        xfun_0.52         tibble_3.3.0     
[51] rstudioapi_0.17.1 sys_3.4.3         knitr_1.50        xtable_1.8-4      htmltools_0.5.8.1
[56] compiler_4.5.2    roxygen2_7.3.2    askpass_1.2.1     openssl_2.3.3    
R: 
R: # extra/libgit2 1:1.9.2-1
```

***


### check `saperlipopette` for goodpractice:

```{r test-goodpractice}
goodpractice::gp(pkg_dir)
```
#### **comments:**

no issues

***

## Check package metadata files

### inspect

- #### [README](https://docs.ropensci.org/saperlipopette/,
    https://github.com/ropensci-training/saperlipopette)
- #### [DESCRIPTION](https://docs.ropensci.org/saperlipopette/,
    https://github.com/ropensci-training/saperlipopette/blob/master/DESCRIPTION)

### spell check

```{r spell-check}
devtools::spell_check(pkg_dir)
```

#### **comments:**

no issues

***

## Review test suite:

### test coverage

```{r pkg_coverage}
covr::package_coverage(pkg_dir)

```

### inspect [tests](https://docs.ropensci.org/saperlipopette/,
    https://github.com/ropensci-training/saperlipopette/blob/master/tests/testthat)


#### **comments:**

Tests have a very similar structure for all the exercises:

eg. test-edit-latest-message.R

```r
rlang::local_options(cli.default_handler = function(msg) invisible(NULL))
parent_path <- withr::local_tempdir()
path <- exo_latest_message(parent_path = parent_path)
expect_identical(fs::path_file(path), "latest-message")
expect_snapshot(gert::git_log(repo = path)[["commit"]])
```

Tests check for 1) the filepath returned from the example function matches the expected filepath name (as in, does `dir_create` create a directory named as expected) and 2) the snapshot of git commit hashes returned from `gert::git_log` match the snapshot. 

It seems that maybe this could be turned into a helper function that might make it simpler for future contributors with new lessons to easily reuse the same testing framework? Here's a quick draft below with an example in my fork of saperlipopette [here](https://github.com/robitalec/saperlipopette/tree/feat/helper-test-exo). 

`tests/testthat/helper-test-exo.R`

```r
helper_test_exo <- function(fn, nm) {
  test_that(paste0(quote(fn), "() works"), {
    rlang::local_options(cli.default_handler = function(msg) invisible(NULL))
    parent_path <- withr::local_tempdir()
    path <- do.call(fn, list(parent_path = parent_path))
    expect_identical(fs::path_file(path), nm)
    expect_snapshot(gert::git_log(repo = path)[["commit"]])
  })
}
```


***


### Reviewer assignment response:


ropensci-training, could you please add the rOpenSci under review badge to your README?
```
[![](https://badges.ropensci.org/754_status.svg)](https://github.com/ropensci/software-review/issues/754)
```

---

Reviewers:
Due date:

***



